% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Shaurya Chawla}

\basicInfo{
  \email{shaurya_ch@outlook.com} \textperiodcentered\ 
  \phone{(+91) 851-086-5767} \textperiodcentered\ 
\basicInfo{
  \faBirthdayCake\ 25/04/1997 \textperiodcentered\ 
  \faHome\ {C-193, Vikaspuri, New Delhi, India}  
}

  

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Maharaja Agrasen Institute of Technology}, New Delhi, India}{2015 -- 2019}
\textit{Bachelor student} in Information Technology Engineering (IT) \textit{72\%} Result Aggregate

\datedsubsection{\textbf{Bal Bharati Public School}, Pitampura, New Delhi, India}{2015}
\textbf{12th} Standard \textit{95\%} Result Aggregate

\datedsubsection{\textbf{Bal Bharati Public School}, Pitampura, New Delhi, India}{2013}
\textbf{10th} Standard \textit{92\%} Result Aggregate

\section{\faUsers\ Experience}

\datedsubsection{\textbf{nTalents.ai} IIM Bangalore, India}{June - July 2018}
\role{Summer Intern}{Manager: Mr. Mayank Sharma}
Brief introduction: Web Development with Flask, React.js and OpenCV.
\begin{itemize}
  \item Implemented Facial Detection using OpenCV.
  \item Changed the existing website.
  \item Converted to React.
  \item Implemented responsive design.
\end{itemize}

\datedsubsection{\textbf{Data Manipulation w/ Python}}{June 2017}
\role{Python, Pandas, Linux}{Individual Projects}
Brief introduction: Learning
\begin{itemize}
  \item Pandas documentation.
  \item Reasearched on suicide rates in India.
  \item Manipulated and predicted future rate of suicides.
  \item Derived conclusions based on data collected.
\end{itemize}

\datedsubsection{\textbf{Website template}}{June 2017}
\role{Maintainer}{Individual Projects}
An elegant website template
\begin{itemize}
  \item Easy to be further customized or extended.
  \item Fully responsive.
\end{itemize}

\datedsubsection{\textbf{WebLook Technologies} New Delhi, India}{July 2016}
\role{Summer Intern}{Manager: Mr. Himanshu}
Brief introduction: Web Development.
\begin{itemize}
  \item Created a website from scratch.
  \item Optimized websites.
  \item Implemented responsive design.
\end{itemize}

\datedsubsection{\textbf{Twitter Bot}}{June 2016}
\role{Python, Django, Linux}{Individual Projects, collaborated with DeastinY}
Brief introduction: Open Source Contributions
\begin{itemize}
  \item Implemented python-based web crawler.
  \item Made compilation scripts.
  \item Twitter bot documentation.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > C++ > Java.
  \item Web Development: ReactJS, Flask, Django, Gulp, Webpack.
  \item Data Manipulation: Pandas, Numpy, Scikitlearn, Matplotlib, Seaborn. 
  \item Platform: Linux, OSX.
  
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{ Participated in}, Hacktoberfest}{Jun. 2016}
\datedline{\textit{ Participated in}, Hacktoberfest}{Jun. 2017}
\datedline{Other awards}{2015}

\section{\faGamepad\ Hobbies/ Other Interests}
\begin{itemize}[parsep=0.5ex]
  \item Playing Guitar - Have pursued professional classes.
  \item Gardening.
  \item Photography.
  \item Sports - Avid football fan.
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://medium.com/@sure\_\_yeah
  \item GitHub: https://github.com/shauryachawla
  \item Languages: English - Fluent, Hindi - Native Speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
